Decoding Consumer Preferences with Large Language Models: A Novel Training Framework

### 2024-06-04 writing/paper.qmd
graph NN

---
author: Finn-Ole Höner (657110)
title: "Decoding Consumer Preferences with Large Language Models: A Novel Training Framework"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 1in
            - bottom = 1in
            - left = 1in
            - right = 1in
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

@@

@@

For a given target sequence, we find the input-embedding that maximizes the likelihood to generate this target sequence with a unidirectional LLM (e.g. GPT, @radford2018improving). We call this input embedding, "summary embedding" of the target sequence.

We restrict the degrees of freedom in our search for these input embeddings, by making the elements of the input embedding linear combinations of a few hidden factors.

@@

- Optimization

@@

- Optimization
  - Computation time, scaling

@@

- Comparison to BERT embeddings
- Comparison to prompt engineering results

@@

@@

- Problems
  - Computation time
  - Benefits over existing approaches in practice?

>>>>

---
author: Finn-Ole Höner (657110)
title: "Decoding Consumer Preferences with Large Language Models: A Novel Training Framework"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \usepackage{tikz}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 1in
            - bottom = 1in
            - left = 1in
            - right = 1in
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

- Neural Text degeneration (@ariholtzmanCuriousCaseNeural2020)
- BERT and RoBERTa @devlinBERTPretrainingDeep2018, @yinhanliuRoBERTaRobustlyOptimized2019, @jeffreypenningtonGloveGlobalVectors2014, @tomasmikolovDistributedRepresentationsWords2013 @tomasmikolovEfficientEstimationWord2013

@@

- Distributional hypothesis of language @sahlgren2008distributional

@@

For a given target sequence, we find the input-embedding that maximizes the likelihood to generate this target sequence with a unidirectional LLM (e.g. GPT, @radford2018improving). We call this input embedding, the "summary embedding" of the target sequence.

We restrict the degrees of freedom in our search for these input embeddings, by making the elements of the input embedding linear combinations of a few hidden factors. This amounts to a linear factor model.

![Factor model in Neural Network form](factor_tikz.tex)

@@

@@

- Optimization
  - @diederikp.kingmaAdamMethodStochastic2014
  - Computation time, scaling
  - Issues with spikes; Figures where they come from

@@

- Comparison to BERT embeddings?
- Comparison to prompt engineering results?

@@

- Costs of tailoring advertising claims
  - When we take current prices for the [GPT-4o LLM; June 2024](https://openai.com/api/pricing/) (\$5 per 1 Mio tokens input, \$15 per 1 Mio tokens output), then training a dataset of 100 advertising claims, for 5,000 epochs will cost \$150. Freelancers on platforms such as [Upwork.com](https://www.upwork.com/) charge between \$20 and \$200 per hour for work on tasks such as SEO optimization, copy writing, and creation of advertising claims.
    - Online services for conjoint studies, such as [Conjointly.com](https://conjointly.com/) and [Sawtooth](https://sawtoothsoftware.com/pricing) charge a few thousand dollars per year to use their services. Leveraging the resulting insights as much as possible, by using generative AI, could hence make market research more cost effective.

@@

- Using embedding rather than identity matrix as the input turns this into an autoencoder, rather than a factor model. According to @goodfellowDeepLearning2016, generation from factor models leads to a combination of the learned features in these factors, but not to the generation of sensible data points. Existing, autoencoder based, approaches that have succeeded in generation tasks, might be more suitable for this task (e.g. CITE: Variational Autoencoder).

- Problems
  - Computation time
  - Benefits over existing approaches in practice?
  - Conceptual issues of using AI in decision making @cathyoneilWeaponsMathDestruction2016; Gender biases @emilyshengWomanWorkedBabysitter2019
  - How to evaluate the quality of the generated ad claims @tatsunorihashimotoUnifyingHumanStatistical2019
